---
title: "The Hangle Algorithm"
author: "Roman Klapaukh & Katie Collins"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Algorithm Explanation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette describes the implementation of the algorithm as implemented in this system. 
This is intended as a reimplementation of the Hangle tool of 
[Haines and Crampton (2000)](http://onlinelibrary.wiley.com/doi/10.1111/1475-4983.00148/abstract).
The algorithm is taken entirely from their work and implemented in the R language.
Any errors in this document or implementation come from our incomplete understanding. 

## Input To The Algorithm

The algorithm takes in a set of points that represent the outline of a closed shape. 
Hangler will check if an outline is closed (the first and last points are the same), 
and if it is remove one of the repeated points.


## Algorithm Overview

The algorith is a pipeline as follows:

   1. Mirror curves where necessary
   1. Ensure that all curves go in the same direction
   1. Remove duplicated xy point that closes the curve if present
   1. Smooth the input coordinates 
   1. Estimate tangents to each coordinate
   1. Compute a spline to model the tangents of the closed curve
   1. Normalise the spline length to $2\pi$
   1. Resample the spline to get 1024 (usually) points
   1. Normalise the starting position and orientation by either:
      * Normalisation by harmonics
      * Normalisation by matching against all speciments
   1. Perform an FFT on the points


There are also helper functions to:

   * Reconstruct the curve from fourier space harmonic coeeficients
   * Draw a curve from its tangents
   
## Smoothing

Smoothing is done by means of a weighed moving averages filter. This filter can be applied multiple times. 

The formula to get a point's smooth location is:

$$
(x,y)_i^{new} = \frac{1}{4}(x,y)_{i-1}^{old} + \frac{1}{2}(x,y)_i^{old} + \frac{1}{4}(x,y)_{i+1}^{old}
$$

Note that since this is a closed curve, given points numbered $0..N,\ (x,y)_{-1} = (x,y)_{N}$.

There is also a minumum number of iterations of the filter that need to be run. 
Given:

   * $N_{Samp}$: the number of sampled xy points in the input
   * $N_{FFT}$: the number of re-sampled points used in the FFT
  
The minimum number of iterations required is: $\frac{2N_{Samp}}{N_{FFT}}$.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
