---
title: "Using Hangler"
author: "Roman Klapaukh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

We are going to run through an example of using hangler to analyse a simple
closed curve shape. 


First we need to generate our data set. This is equivalent to a human digitising
a curve. We come out with only a set of xy coordinates sampled along the shape. 

```{r}
library(hangler)
```

```{r}
theta = seq(0,2*pi, 0.001)

radius = 6

wiggle1 = 7
wiggle2 = 3

x = (cos(3*theta*wiggle2) + sin(theta*wiggle1) + radius) * cos(theta)
y = (cos(3*theta*wiggle2) + sin(theta*wiggle1) + radius) * sin(theta)

rm(theta)
rm(wiggle1)
rm(wiggle2)
rm(radius)
```

We can now plot it and see our apeture.

```{r fig.caption="The base closed curve"}
plot(x,y,col="black")
lines(c(x,x[1]),c(y,y[1]),col="blue")
```

We now get the tangets.

```{r}
tangents = computeTangents(x,y)
```

Now we can plot the tangents and notice that the tangent curve we get is 
nice and continuous.

```{r}
plot(tangents)
lines(tangents,col="blue")
```

We can plot them on the original shape to see that they make sense.

```{r}
plot(x,y,col="black")
lines(c(x,x[1]),c(y,y[1]),col="blue")
for(i in 1:length(x)){
  dtx = cos(tangents[i])
  dty = sin(tangents[i])
  lines(c(x[i] - dtx,x[i]+dtx),y=c(y[i] - dty,y[i]+dty),col="purple")
}
```

At this point we *could* resample. But that bit doesn't always work yet. 

We can now run the FFT over the [resampled] spline. 

```{r}
coeffs = fft(tangents)/length(tangents)
```

We start by taking only the first 30 and now trying to reconstruct the original
curve. 

```{r}
coeffs = coeffs[1:300]
```


We now want to go back from fft coefficients to fft parameters to go backwards.

```{r}
backCoeffs = fftoToCoeffs(coeffs)
```

Now we can reconstruct the original curve. 

```{r}
reconstructedTangents = sapply(seq(0,2*pi,length.out=length(tangents)),
      function(s) getTangentAtS(s,backCoeffs))

with(tangentsToXY(reconstructedTangents), {plot(x, y,col=rainbow(256)); lines(x,y)})
```
