---
title: "Using Hangler"
author: "Roman Klapaukh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=5, fig.height=5) 
```

We are going to run through an example of using hangler to analyse a simple
closed curve shape. 


First we need to generate our data set. This is equivalent to a human digitising
a curve. We come out with only a set of xy coordinates sampled along the shape. 

```{r}
library(hangler)
```

```{r}
theta = seq(0,2*pi, 0.01)

radius = 6

wiggle = 7

x = (sin(theta*wiggle) + radius) * cos(theta)
y = (sin(theta*wiggle) + radius) * sin(theta)

rm(theta)
rm(wiggle)
rm(radius)
```

We can now plot it and see our apeture.

```{r fig.caption="The base closed curve"}
plot(x,y,col="black")
lines(c(x,x[1]),c(y,y[1]),col="blue")
```

We now get the tangets.

```{r}
tangents = computeTangents(x,y)
```

Now we can plot the tangents and notice that the tangent curve we get is 
nice and continuous.

```{r}
plot(tangents)
lines(tangents,col="blue")
```

We can turn them back into a shape and see that they give the original.

```{r}
with(tangentsToXY(tangents), {
   plot(x, y,col=rainbow(length(tangents))); 
   lines(x,y)
})
```

At this point we need to resample the tangent curve. 
This is because FFT requires evenly spaced points, but we cannot be certain
that our digitisation / landmark capture is even along the curve length. 
We will resample the default number of points. 

```{r}
newTangents = resampleTangents(x,y, tangents)
```

We can now plot our new tangents to make sure they are the same as the old ones.

```{r}
plot(newTangents)
lines(newTangents,col="blue")
```

That done, we now need to remove the normal shift associated with a unit circle. 
Hangle characterises shape by deviation from unit circle rather than directly.

```{r}
newTangents = flattenTangents(newTangents)
```

Now we can plot the results to make sure they look sensible (like a 
wave). 


```{r}
plot(newTangents)
lines(newTangents,col="blue")
```

From this point one we can get our coefficients by using R's inbuilt FFT. 

```{r}
coeffs = fft(newTangents)/length(newTangents)
```


We start by taking only the first 30 and now trying to reconstruct the original
curve. 

```{r}
coeffs = coeffs[1:30]
```


We now want to go back from fft coefficients to fft parameters to go backwards.

```{r}
backCoeffs = fftoToCoeffs(coeffs)
```

Now we can reconstruct the original curve. 

```{r}
reconstructedTangents = sapply(seq(0,2*pi,length.out=length(newTangents)),
      function(s) getTangentAtS(s,backCoeffs))
```

We can now look at the reconstructed tangents and compare them to the originals


```{r}
plot(reconstructedTangents)
lines(reconstructedTangents,col="blue")
```

And now reconstruct the curve

```{r}
with(tangentsToXY(reconstructedTangents), {
   plot(x, y,col=rainbow(length(newTangents))); 
   lines(x,y)
})
```
